---
title: "Final report"
author: "Bailey Lei, George J. J. Wu"
date: "November 22, 2018"
output: github_document
---

```{r echo = FALSE}
suppressPackageStartupMessages(library()
```


Chocolate bar is one of the most popular treats around the world, but not all chocolate bars are made the same. Some chocolate bars are more concentrated in terms of cocoa and are more bitter, while some chocolate bars are less concentrated and are lighter flavoured.

This begs a question - are chocolate bars that are more concentrated also means that they are simply better chocolate bars? In other words, are chocolate bars that are 99% pure better than chocolate bars that are only 79% pure?  

This analysis will explore the relationship between chocolate darkness (cocoa percentage) and chocolate expert ratings.

#### Data set

We will examine the expert ratings of 1,795 chocolate bars that were compiled by Brady Brelinski, a Founding Member of the [Manhattan Chooclate Society](http://flavorsofcacao.com/index.html). This data set is hosted on [Kaggle](https://www.kaggle.com/rtatman/chocolate-bar-ratings). 

We are only interested in two variables in the data - cocoa percentage (chocolate darkness) and expert ratings.

```{r}
# load data
coco <- read_csv("..data/cleaned_coca.csv")
```




